%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://ecuafirma.com}{EcuaFirma}: PDF digital signature system.} % Project
    {At \href{https://touwolf.com/}{Touwolf Technologies S.A.}} % Company
    {Quito, Ecuador} % Location
    {Apr. 2020 - Actual} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL.}
        \item {Backend server using Java (Spring Boot).}
        \item {REST API server using Java (Spring Boot).}
        \item {Mobile App for several platforms: Android, iOS (Flutter).}
        \item {PDF signing with electronic signature files (.p12, .pfx).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.ccffaa.mil.ec/}{Command of the Armed Forces of Ecuador}: Mobile application.} % Project
    {} % Company
    {} % Location
    {Dec. 2019 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Frontend clients for several platforms (Android, iOS) using Flutter.}
        \item {Push Notifications for Android and iOS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {WooCommerce: APP cliente.} % Project
    {} % Company
    {} % Location
    {Ene. 2020 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Frontend for several platforms (Android, iOS) using Flutter.}
        \item {WooCommerce API Rest integration.}
        \item {Users access.}
        \item {List, search and selection of categories and products.}
        \item {Shopping cart management.}
        \item {Plugin for integration with WooCommerce (PHP).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Datafast: Plugin for integration with WooCommerce.} % Project
    {} % Company
    {} % Location
    {Sep. 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Online payments using payment gateway. (Datafast).}
        \item {Plugin for integration with WooCommerce (PHP).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://tufacturero.ec}{TuFacturero}: Invoicing system.} % Project
    {} % Company
    {} % Location
    {Apr. 2017 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL, MongoDB and RedisDB.}
        \item {Backend server using Java.}
        \item {REST API server using Java.}
        \item {Frontend clients for several platforms (HTML5, React, Android, iOS).}
        \item {Online payments using several payment gateways (Paymentez, Datafast).}
        \item {SOAP client for SRI Ecuador system API.}
        \item {Push notifications for Android and iOS.}
        \item {Plugin for integration with WooCommerce (PHP).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://tappetit.com}{Tappetit}: Restaurant management system.} % Project
    {} % Company
    {} % Location
    {Apr. 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL and RedisDB.}
        \item {Backend server using Java.}
        \item {Authentication with fingerprint recognition.}
        \item {Electronic payments with Datafast POS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://telemedico.com.ec/}{Telemédico}: Telemedicine system.} % Project
    {} % Company
    {} % Location
    {Jul. 2019 - Current} % Date(s))
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL.}
        \item {Cloud storage using Amazon S3.}
        \item {Backend server using Loopback 3 (nodejs).}
        \item {Frontend using React and React native (Android, iOS, Web \& Admin).}
        \item {Video calls using Agora.}
        \item {Online payment using Paymentez.}
        \item {Push notifications for Android and iOS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://showshop.app/}{Showshop}: Online store system.} % Project
    {} % Company
    {} % Location
    {Jul. 2019 - Jan. 2020} % Date(s))
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using Firebase Functions.}
        \item {Frontend using Flutter (Android, iOS).}
        \item {Frontend using React (Admin).}
        \item {Store administration.}
        \item {Instant messaging.}
        \item {Maps for access to stores and location (customer tracking).}
        \item {Push notifications for Android and iOS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://aquiquehay.com.ec/}{AquiQueHay}: Social aplication.} % Project
    {} % Company
    {} % Location
    {Dec. 2017 - Jan. 2019} % Date(s))
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL.}
        \item {Frontend for several platforms (Android, iOS).}
        \item {Push notifications for Android and iOS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.cuballama.com/viajes/vuelos}{Cubaviaja}: Booking system.} % Project
    {} % Company
    {} % Location
    {Apr. 2015 - Oct.2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL and RedisDB.}
        \item {Backend server using Java.}
        \item {Frontend for several platforms (HTML5, Android, iOS).}
        \item {Online payment using several gateways (Braintree, EBanx, PayPal).}
        \item {Push notifications for Android and iOS.}
        \item {SOAP client for booling using Amadeus API.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.cuballama.com/}{Cuballama}: Management system for telecommunications platform and online payments.} % Project
    {} % Company
    {} % Location
    {Apr. 2014 - Oct.2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Database infrastructure using MySQL and RedisDB.}
        \item {Backend server using Java and PHP.}
        \item {Frontend for several platforms (Angular, Ionic, Android, iOS).}
        \item {Online payment using several payment gateways (Braintree, BeanStream, EBanx, PayPal).}
        \item {Voice calls using WebRTC on Web, Android and iOS platforms.}
        \item {SMS messaging system using several APIs (Nexmo, Twilio).}
        \item {Push notifications for Android and iOS.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
