%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Activity}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Owner} % Affiliation/role
    {\href{https://github.com/zp1ke/salert}{Salert Dart library}} % Organization/group
    {\href{https://pub.dev/packages/salert}{Pub Package}} % Location
    {May. 2024 - Actual} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {A library for efficient sales amounts calculations, including discounts, subtotal before taxes, taxes and total amounts}
        \item {Used in {\href{https://eqon.ec/}{eQon}} app.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {\href{https://github.com/jambodb/jambodb-storage}{JamboDB Storage engine}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Dec. 2021 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Storage engine to be use in JamboDB database projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {\href{https://github.com/touwolf/bridje-framework}{Bridje Java Framework}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {May. 2016 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Set of APIs to be use in Java projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contribution to official repository \href{https://github.com/xdan/jodit}{Jodit - WYSIWYG Editor}} % Affiliation/role
    {\href{https://github.com/zp1ke/jodit}{Jodit - WYSIWYG Editor}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Jun. 2018 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Spanish language support.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Owner} % Affiliation/role
    {\href{https://github.com/zp1ke/jasperreport-maven-plugin}{Jasper Report Maven Plugin}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Mar. 2018 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Plugin to integrate JasperReport templates in maven builds.}
        \item {Compiles .jasper templates from .jrxml files}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contribution to official repository \href{https://github.com/googlemaps/google-maps-ios-utils}{Utility library for Google Maps SDK for iOS}} % Affiliation/role
    {\faMapMarker \hphantom{-} \href{https://github.com/zp1ke/google-maps-ios-utils}{Utility library for Google Maps SDK for iOS}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Dec. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Fixed background colors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Owner} % Affiliation/role
    {\href{https://github.com/zp1ke/deps-checker}{IntelliJ IDEA / Dependencies Checker Plugin}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Jan. 2017 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {\href{https://plugins.jetbrains.com/plugin/9481-java-dependencies-checker}{Jetbrains IDE plugin}.}
        \item {Checks Java projects dependencies to update their versions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Owner} % Affiliation/role
    {\faMobile \hphantom{-} \href{https://github.com/zp1ke/taresip}{Cocoapod for baresip}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Apr. 2016 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Cocoapod for baresip library (SIP User-Agent with audio and video support for iOS).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {\href{https://github.com/touwolf/kasije}{Kasije CMS}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Feb. 2016 - May. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Project for \href{https://www.koding.com/Hackathon}{koding Hackathon}.}
        \item {CMS to host multiple websites from a single location, with declarative content and shared resources.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contribution to official repository \href{https://github.com/paypal/PayPal-Cordova-Plugin}{PayPal SDK Cordova/Phonegap Plugin}} % Affiliation/role
    {\faPaypal \hphantom{-} \href{https://github.com/zp1ke/PayPal-Cordova-Plugin}{PayPal SDK Cordova/Phonegap Plugin}} % Organization/group
    {\faGithubSquare\acvHeaderIconSep Github} % Location
    {Oct. 2014 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Added option to include invoice number in PayPalPayment.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
